MolProbity's Ultimate Rotamer-Library Distributions for Model Validation

### 2016-02-24 discussion.tex
Fixed rotamer boldface in discussion, shoild include the numbers

The contour values in our rotamer distributions correspond to the percentage of high-quality reference data that lies outside that contour. The consequence of this treatment is that the contour data represent a probability density function in $\chi$ space describing sidechain conformations. We recommend using those contours to delimit sampling or minimization in $\chi$ space, with the added benefit that the contour levels provide prior probabilities for each position. If a contour level higher than 0.3\% is chosen \textcolor{changecolor}{to limit sampling within a rotamer well}, then entire rotamers which do not reach the chosen percentage level should also be omitted. Depending on details of the algorithm used, it may or may not be beneficial to model significant rotamer-dependent bond-angle deviations. \textcolor{changecolor}{It should also be noted that some rotamer wells are very elongated, and if minimization is only allowed to move by a fixed distance from the central value, then additional sample points may need to be defined.  Elongated rotamers only occur when the final $\chi$ angle is around a tetrahedral-to-planar bond, easily recognizable because the rotamer name ends in a number (e.g., Trp \textbf{t}160 or Arg \textbf{ppp}-140).}

>>>>

The contour values in our rotamer distributions correspond to the percentage of high-quality reference data that lies outside that contour. The consequence of this treatment is that the contour data represent a probability density function in $\chi$ space describing sidechain conformations. We recommend using those contours to delimit sampling or minimization in $\chi$ space, with the added benefit that the contour levels provide prior probabilities for each position. If a contour level higher than 0.3\% is chosen \textcolor{changecolor}{to limit sampling within a rotamer well}, then entire rotamers which do not reach the chosen percentage level should also be omitted. Depending on details of the algorithm used, it may or may not be beneficial to model significant rotamer-dependent bond-angle deviations. \textcolor{changecolor}{It should also be noted that some rotamer wells are very elongated, and if minimization is only allowed to move by a fixed distance from the central value, then additional sample points may need to be defined.  Elongated rotamers only occur when the final $\chi$ angle is around a tetrahedral-to-planar bond, easily recognizable because the rotamer name ends in a number (e.g., Trp \textbf{t160} or Arg \textbf{ppp-140}).}
